Supplementary Material for Asymmetry paper

### 2020-07-10 Supplementary/Sup_mat.Rmd
Updates to figures

``` {r HS_Prior, include = T, echo = F}
HS_prior <- c(set_prior("student_t(3, 0, 1)",
                        coef = "norm_hoop_pos",
                        class = "b"),
              set_prior("student_t(3,0,1)",
                        class = "Intercept"))
```

@@

```{r run-model-hoop-size-priors, echo = T, include = T, message = F, warning = F, results = "hide", cache = TRUE}
# run model
Hoop_size_priors <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                        data = model_data,
                        family = "beta",
                        prior = HS_prior,
                        cores = 2,
                        chains = 2,
                        iter = 5000,
                        warmup = 2500,
                        control = list(adapt_delta = .95, max_treedepth = 15),
                        sample_prior = "only")
```

@@

```{r run-model-Hoop-size, include = T, echo = T, message = F, warning = F, results = "hide", cache = TRUE}
# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                    data = model_data,
                    family = "beta",
                    prior = HS_prior,
                    cores = 2,
                    chains = 2,
                    iter = 5000,
                    warmup = 2500,
                    control = list(adapt_delta = .95, max_treedepth = 15))

@@

```{r PltHoopSizeEstimates, include = F, echo = F, fig.asp=.45, fig.cap="_Posterior predictions for the mean standing position._"}
plt_post_hoopsize <- draws$plt_estimates + 
  scale_x_continuous(expression(paste("Normalised ", Delta)), 
                     breaks = c(0,.5,1),
                     labels = c("Big Hoop", "Centre", "Small Hoop")) + 
  theme(legend.position = "bottom")
```

@@

priors_plt <- draws_df$Draws_df %>%
  mutate(prop = boot::inv.logit(estimate),
         Dist_type = factor(Dist_type, c("Close", "Mid", "Far"))) %>% 
  ggplot(aes(prop,colour = Num_throws, fill = Num_throws)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous(expression(paste("Normalised ", Delta))) +
  geom_density(kernel = "biweight", alpha = .3) + 
  facet_wrap(~Dist_type) + 
  theme_bw() + 
  guides(fill = guide_legend(title = "No. Throws"),
         colour = guide_legend(title = "No. Throws")) +
  theme(legend.position = "bottom")

@@

```{r PltTwoThrowEstimates, include = F, echo = F}
# get draws
draws <- draw_post_delta(Two_throw_m1, model_data_pos)
# example distributions 
plt_examples <- draws$Plots[1][[1]][["data"]] %>% 
  mutate(Dist_Type = factor(Dist_type, c("Close", "Mid", "Far"))) %>% 
  ggplot(aes(prop, 
             colour = Num_throws,
             fill = Num_throws)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  facet_wrap(~Dist_Type) + 
  theme_bw() + 
  scale_x_continuous(expression(paste("Normalised ", Delta))) + 
  coord_cartesian(expand = F) + 
  guides(fill = guide_legend(title = "No. Throws"),
         colour = guide_legend(title = "No. Throws")) +
  theme(legend.position = "bottom")

# plt_difference 
plt_difference <- draws$Plots[3][[1]][["data"]] %>%
  mutate(Dist_type = as.factor(Dist_type)) %>%
  mutate(Dist_type = factor(Dist_type, c("Close", "Mid", "Far"))) %>% 
  ggplot(aes(diff,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  # see::scale_color_flat() + 
  # see::scale_fill_flat() + 
  scale_fill_viridis_d() + 
  scale_colour_viridis_d() +
  scale_x_continuous("Difference: One throw - Two throw") +
  guides(fill = guide_legend(title = "Distance"),
         colour = guide_legend(title = "Distance"))

@@

```{r TwoThrowPlts, include = T, echo = F, fig.asp = .65, fig.cap = "_The panel shows the Prior preditcions for the Two Throw experiment. The middle panel shows the Posterior predictions for the Two Throw expeirment. The bottom panel shows the difference between One and Two throw conditions across the same distances shown in the other panels_"}
# get legend 
TwoThrowLegend <- g_legend(priors_plt)

grid.arrange(arrangeGrob(priors_plt + theme(legend.position = "none"), plt_examples + theme(legend.position = "none")),
                     TwoThrowLegend, plt_difference, heights=c(10, 1, 5))

@@

@@

``` {r RewardPriorsPlt, include = T, echo = F, fig.asp = .45, fig.cap = "_Prior Predictions for the Reward Study_"}
draws_factor(Reward_priors) %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  ggplot(aes(prop,
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  geom_density(alpha = .3,
               kernel = "biweight") +
  scale_x_continuous(expression(paste("Normalised ", Delta))) +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  facet_wrap(~Dist_Type) + 
  theme_bw()
```

The priors for this model were set to be roughly flat and uniformative to reflect the uncertainty around the outcomes of this experiment. Until this experiment, we had not run a version of this task in which the different targets could have different value associtated with them.

@@

plt_inter <- draws_df %>%
  ggplot(aes(prop, 
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  scale_x_continuous(expression(paste("Normalised ", Delta))) + 
  facet_wrap(~Dist_Type)

@@

```{r PltRewardestimates, echo = F, include = T, warning = F, fig.asp=.45, fig.cap="_This plot shows the posterior distribution of standing positions for the Reward study_"}
# gridExtra::grid.arrange(plt_dist, bottom, heights = c(2, 4))
plt_inter
```

>>>>

``` {r HS_Prior, include = T, echo = F}
HS_prior <- c(set_prior("student_t(3, 0, 1)",
                        coef = "norm_hoop_pos",
                        class = "b"),
              set_prior("student_t(3,0,1)",
                        class = "Intercept"))
HS_iter <- 5000
HS_control <- list(adapt_delta = .95, max_treedepth = 15)
```

@@

```{r run-model-hoop-size-priors, echo = T, include = T, message = F, warning = F, results = "hide", cache = TRUE}
# run model
Hoop_size_priors <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                        data = model_data,
                        family = "beta",
                        prior = HS_prior,
                        cores = 2,
                        chains = 2,
                        iter = HS_iter,
                        warmup = HS_iter/2,
                        control = HS_control,
                        sample_prior = "only")
```

@@

```{r run-model-Hoop-size, include = T, echo = T, message = F, warning = F, results = "hide", cache = TRUE}
# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
                    data = model_data,
                    family = "beta",
                    prior = HS_prior,
                    cores = 2,
                    chains = 2,
                    iter = HS_iter,
                    warmup = HS_iter/2,
                    control = HS_control)

@@

```{r PltHoopSizeEstimates, include = F, echo = F, fig.asp=.45, fig.cap="_Posterior predictions for the mean standing position._"}
plt_post_hoopsize <- draws$plt_estimates + 
  scale_x_continuous(expression(paste("Normalised ", Delta)),
                     limits = c(0,1),
                     breaks = c(0,.5,1),
                     labels = c("Big Hoop", "Centre", "Small Hoop")) + 
  theme(legend.position = "bottom")
```

@@

priors_plt <- draws_df$Draws_df %>%
  mutate(prop = boot::inv.logit(estimate),
         Dist_type = factor(Dist_type, c("Close", "Mid", "Far"))) %>% 
  ggplot(aes(prop,colour = Num_throws, fill = Num_throws)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous(expression(paste("Normalised ", Delta)),
                     limits = c(-.1,1.1),
                     breaks = seq(0,1,.25)) +
  geom_density(kernel = "biweight", alpha = .3) + 
  facet_wrap(~Dist_type) + 
  theme_bw() + 
  guides(fill = guide_legend(title = "No. Throws"),
         colour = guide_legend(title = "No. Throws")) +
  theme(legend.position = "right")

@@

```{r PltTwoThrowEstimates, include = F, echo = F}
# get draws
draws <- draw_post_delta(Two_throw_m1, model_data_pos)
# example distributions 
plt_examples <- draws$Plots[1][[1]][["data"]] %>% 
  mutate(Dist_Type = factor(Dist_type, c("Close", "Mid", "Far"))) %>% 
  ggplot(aes(prop, 
             colour = Num_throws,
             fill = Num_throws)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  facet_wrap(~Dist_Type) + 
  theme_bw() + 
  scale_x_continuous(expression(paste("Normalised ", Delta)),
                     limits = c(-.1,1.1),
                     breaks = seq(0,1,.25)) + 
  coord_cartesian(expand = F) + 
  guides(fill = guide_legend(title = "No. Throws"),
         colour = guide_legend(title = "No. Throws")) +
  theme(legend.position = "right")

# plt_difference 
plt_difference <- draws$Plots[3][[1]][["data"]] %>%
  mutate(Dist_type = as.factor(Dist_type)) %>%
  mutate(Dist_type = factor(Dist_type, c("Close", "Mid", "Far"))) %>% 
  ggplot(aes(diff,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  geom_vline(xintercept = 0,
             linetype = "dashed") +
  # see::scale_color_flat() + 
  # see::scale_fill_flat() + 
  scale_fill_viridis_d() + 
  scale_colour_viridis_d() +
  scale_x_continuous("Difference: One throw - Two throw") +
  guides(fill = guide_legend(title = "Distance"),
         colour = guide_legend(title = "Distance"))

@@

```{r TwoThrowPlts, include = T, echo = F, fig.asp = .45, fig.cap = "_The top panel shows the Prior preditcions for the Two Throw experiment. The bottom panel shows the Posterior predictions for the Two Throw expeirment._"}
# get legend 
TwoThrowLegend <- g_legend(priors_plt)

grid.arrange(arrangeGrob(priors_plt + theme(legend.position = "none"), plt_examples + theme(legend.position = "none")),
             TwoThrowLegend, ncol = 2, widths=c(6, 1))

@@

```{r TwoThrowDifference, include = T, echo = F, fig.asp = .45, fig.cap = "_This figure shows the difference in the estimates for the Two Throw experiment. This is the diffrence between the red and blue distributions see in the Figure `@ref(fig:TwoThrowPlts)` with a bigger number representing the One Throw condition have a larger mean than the Two Throw condition._"}
plt_difference
```

@@

``` {r RewardPriorsPlt, include = F, echo = F}
plt_RewardPriors <- draws_factor(Reward_priors) %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  ggplot(aes(prop,
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  geom_density(alpha = .3,
               kernel = "biweight",
               bw = .1) +
  scale_x_continuous(expression(paste("Normalised ", Delta)),
                     limits = c(-.1, 1.1),
                     breaks = seq(0,1,.25)) +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  facet_wrap(~Dist_Type) + 
  theme_bw()
```

The priors in for this model were set so as to reduce the likelihood of extreme values (i.e., close to 0% or 100%). Until this experiment, we had not run a version of this task in which the different targets could have different value associtated with them.

@@

plt_inter <- draws_df %>%
  ggplot(aes(prop, 
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  scale_x_continuous(expression(paste("Normalised ", Delta)),
                     limits = c(-.1, 1.1),
                     breaks = seq(0,1,.25)) + 
  facet_wrap(~Dist_Type)

@@

```{r PltRewardestimates, echo = F, include = T, warning = F, fig.asp=.45, fig.cap="_This plot shows the posterior distribution of standing positions for the Reward study_"}
grid.arrange(arrangeGrob(plt_RewardPriors + theme(legend.position = "none"), plt_inter + theme(legend.position = "none")), Reward_legend, ncol = 2, widths = c(6,1))
#plt_inter
```
